---
title: "R Notebook"
output: html_notebook
---
libraries
```{r}
library(mlbench)
library(dplyr)
library(lubridate)
library(ggplot2)
library(factoextra)
library(sets)
library(ggcorrplot)
```
Data description:

crim	per capita crime rate by town
zn	proportion of residential land zoned for lots over 25,000 sq.ft
indus	proportion of non-retail business acres per town
chas	Charles River dummy variable (= 1 if tract bounds river; 0 otherwise)
nox	nitric oxides concentration (parts per 10 million)
rm	average number of rooms per dwelling
age	proportion of owner-occupied units built prior to 1940
dis	weighted distances to five Boston employment centres
rad	index of accessibility to radial highways
tax	full-value property-tax rate per USD 10,000
ptratio	pupil-teacher ratio by town
b	1000(B - 0.63)^2 where B is the proportion of blacks by town
lstat	percentage of lower status of the population
medv	median value of owner-occupied homes in USD 1000's
cmedv	corrected median value of owner-occupied homes in USD 1000's
town	name of town
tract	census tract
lon	longitude of census tract
lat	latitude of census tract
```{r}
data(BostonHousing2)
```

Check if there is any missing value from data
```{r}
s = 0
for(i in BostonHousing2){
  if(is.null(i)){
    s = s + 1
  }
}
print(paste("Missing values: ", s))
```

Density plots
```{r}
ggplot(BostonHousing2, aes(x = cmedv)) + geom_histogram(bins = 30, aes(y = stat(density))) + geom_density(col="red")
```
Create a variable with all values in numeric type
```{r}
bostonHousingAllNumeric = BostonHousing2

bostonHousingAllNumeric$town = as.numeric(bostonHousingAllNumeric$town)
bostonHousingAllNumeric$chas = as.numeric(bostonHousingAllNumeric$chas)

bostonHousingAllNumeric
```


Correlation Matrix
```{r}
ggcorrplot(cor(bostonHousingAllNumeric), lab = TRUE, lab_size = 3)
```
Scatter Plot for rm
```{r}
ggplot(bostonHousingAllNumeric, aes(x = rm, y = cmedv)) + geom_point()
```

Scatter plot for lstat
```{r}
ggplot(bostonHousingAllNumeric, aes(x = lstat, y = cmedv)) + geom_point()
```

